### 2022-07-15 manuscript.Rmd
Update for re-submission

authornote: |
  We have no conflicts of interest to disclose.
  The data and code for this study are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).

@@

As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Figure\ \@ref(fig:fig2)). Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_reg$male_female`$ (where $b = \Delta{g}$), 95% CrI [`r summ_reg$male_female.lower`, `r summ_reg$male_female.upper`]. The probability for this effect being larger than zero was `r print_prob(hyps_brm_reg$male_female$Post.Prob)`. We found no difference between mixed-gender and all-female samples, $b = `r -summ_reg$female_mixed`$, 95% CrI [`r -summ_reg$female_mixed.lower`, `r -summ_reg$female_mixed.upper`] (`r print_prob(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero). Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_reg$age`$, 95% [`r summ_reg$age.lower`, `r summ_reg$age.upper`]. We also did not detect an interaction between gender and age ([females - mixed] $\times$ age: $b = `r summ_reg$female_mixed_age`$, 95% CrI [`r summ_reg$female_mixed_age.lower`, `r summ_reg$female_mixed_age.upper`]; [males - females] $\times$ age: $b = `r summ_reg$male_female_age`$, 95% CrI [`r summ_reg$male_female_age.lower`, `r summ_reg$male_female_age.upper`]). Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_reg$voe_habituation`$, 95% [`r summ_reg$voe_habituation.lower`, `r summ_reg$voe_habituation.upper`]. The probability for this effect being greater than zero was `r print_prob(hyps_brm_reg$voe_habituation$Post.Prob)`.

@@

# Define new labels for the regression coefficients
coef_colnames <- c(
  b_Intercept = expression("Intercept (Hedges" ~ italic(g) * ")"),
  b_gender2M1 = expression("Females - mixed"),
  b_gender3M2 = expression("Males - females"),
  b_age_c = expression("Age (per year)"),
  b_task2M1 = expression("Habituation - VoE"),
  `b_gender2M1:age_c` = expression("(Females - Mixed)" %*% "age"),
  `b_gender3M2:age_c` = expression("(Males - Females)" %*% "age")
)

@@

(ref:fig2-caption) **Effects of gender, age, and task.** (A) Squares show the effect size (Hedges' $g$) for infants' mental rotation performance in each of the 59 individual experiments. Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample, yellow = habituation task, all-male sample, red = habituation task, mixed-gender sample, purple = violation of expectation [VoE] task, mixed-gender sample). Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 50% and 95% credible interval (CrI). (B) Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 50% CrI (thick black lines) and 95% CrI (thin black lines). Gray curves indicate the posterior distribution for each effect.

@@

We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature included here. For the meta-analysis of mental rotation performance (Figure\ \@ref(fig:fig3)a), we observed a slight asymmetry in the funnel plot, indicating a small publication bias. This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $p = `r print_p(egger_meta$pval)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test). Nevertheless, a jackknife (leave-one-out) analysis confirmed that the current results are robust to the effects of individual outlier experiments (Supplementary Table\ \@ref(tab:tabs3)). For the meta-analysis of gender differences in mental rotation performance (Figure\ \@ref(fig:fig3)b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% CI [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).

@@

    # Plot the funnels
    ggplot(dat, aes(x = gi, y = sei)) +
      # Funnels under the null hypothesis
      geom_polygon(data = funnel_smaller_01, aes(x = x, y = y, fill = level)) +
      geom_polygon(data = funnel_smaller_05, aes(x = x, y = y, fill = level)) +
      geom_polygon(data = funnel_greater_05, aes(x = x, y = y, fill = level)) +
      scale_fill_manual(
        values = c("gray80", "grey90", "white"),
        breaks = c("greater_05", "smaller_05", "smaller_01"),
        labels = c(
          expression(italic(P) > 0.05),
          expression(italic(P) < 0.05),
          expression(italic(P) < 0.01)
        )
      ) +
      # Grid lines
      geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
      # Observed_funnel
      geom_path(data = funnel_observed, aes(x = x, y = y)) +
      # Meta-analytic effect size
      geom_vline(xintercept = summ$intercept, color = "black") +
      # Experiment-specific effect sizes
      geom_point(shape = 0) +
      # Styling
      scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
      scale_y_reverse() +
      coord_cartesian(
        xlim = c(-2.5, 2.5),
        ylim = c(max_se, 0),
        expand = FALSE
      ) +
      labs(
        x = expression("Hedges'" ~ italic("g")), y = "Standard error",
        fill = "Significance level"
      ) +
      theme_classic() +
      theme(
        axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "Helvetica", color = "black"),
        axis.ticks = element_line(color = "black"),
        legend.position = "none",
        text = element_text(family = "Helvetica", color = "black")
      )
  }
) -> plots_funnel

@@

## Transparency and openness

The data and code for this study are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e). This study was not preregistered.

>>>>

authornote: |
  We have no conflicts of interest to disclose.
  The data and code necessary to reproduce the analyses presented here are publicly accessible at the following URL: [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).
  The analyses presented here were not preregistered.

@@

As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Figure\ \@ref(fig:fig2)). Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_reg$male_female`$ (where $b = \Delta{g}$), 95% CrI [`r summ_reg$male_female.lower`, `r summ_reg$male_female.upper`]. The probability for this effect being larger than zero was `r print_prob(hyps_brm_reg$male_female$Post.Prob)`. We found no difference between mixed-gender and all-female samples, $b = `r -summ_reg$female_mixed`$, 95% CrI [`r -summ_reg$female_mixed.lower`, `r -summ_reg$female_mixed.upper`] (`r print_prob(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero). Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_reg$age`$, 95% CrI [`r summ_reg$age.lower`, `r summ_reg$age.upper`]. We also did not detect an interaction between gender and age ([females - mixed] $\times$ age: $b = `r summ_reg$female_mixed_age`$, 95% CrI [`r summ_reg$female_mixed_age.lower`, `r summ_reg$female_mixed_age.upper`]; [males - females] $\times$ age: $b = `r summ_reg$male_female_age`$, 95% CrI [`r summ_reg$male_female_age.lower`, `r summ_reg$male_female_age.upper`]). Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_reg$voe_habituation`$, 95% CrI [`r summ_reg$voe_habituation.lower`, `r summ_reg$voe_habituation.upper`]. The probability for this effect being greater than zero was `r print_prob(hyps_brm_reg$voe_habituation$Post.Prob)`.

@@

# Define new labels for the regression coefficients
coef_colnames <- c(
  b_Intercept = expression("Intercept (Hedges'" ~ italic(g) * ")"),
  b_gender2M1 = expression("Females - mixed"),
  b_gender3M2 = expression("Males - females"),
  b_age_c = expression("Age (per year)"),
  b_task2M1 = expression("Habituation - VoE"),
  `b_gender2M1:age_c` = expression("(Females - Mixed)" %*% "age"),
  `b_gender3M2:age_c` = expression("(Males - Females)" %*% "age")
)

@@

(ref:fig2-caption) **Effects of gender, age, and task.** (A) Squares show the effect size (Hedges' $g$) for infants' mental rotation performance in each of the 59 individual experiments. Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample; yellow = habituation task, all-male sample; red = habituation task, mixed-gender sample; purple = violation of expectation [VoE] task, mixed-gender sample). Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 50% and 95% credible interval (CrI). (B) Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 50% CrI (thick black lines) and 95% CrI (thin black lines). Gray curves indicate the posterior distribution for each effect.

@@

We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature included here. For the meta-analysis of mental rotation performance (Figure\ \@ref(fig:fig3)A), we observed a slight asymmetry in the funnel plot, indicating a small publication bias. This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $p = `r print_p(egger_meta$pval)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test). Nevertheless, a jackknife (leave-one-out) analysis confirmed that the current results are robust to the effects of individual outlier experiments (Supplementary Table\ \@ref(tab:tabs3)). For the meta-analysis of gender differences in mental rotation performance (Figure\ \@ref(fig:fig3)B), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% CI [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).

@@

    # Plot the funnels
    ggplot(dat, aes(x = gi, y = sei)) +
      # Funnels under the null hypothesis
      geom_polygon(data = funnel_smaller_01, aes(x = x, y = y, fill = level)) +
      geom_polygon(data = funnel_smaller_05, aes(x = x, y = y, fill = level)) +
      geom_polygon(data = funnel_greater_05, aes(x = x, y = y, fill = level)) +
      scale_fill_manual(
        values = c("gray80", "grey90", "white"),
        breaks = c("greater_05", "smaller_05", "smaller_01"),
        labels = c(
          expression(italic(p) > 0.05),
          expression(italic(p) < 0.05),
          expression(italic(p) < 0.01)
        )
      ) +
      # Grid lines
      geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
      # Observed_funnel
      geom_path(data = funnel_observed, aes(x = x, y = y)) +
      # Meta-analytic effect size
      geom_vline(xintercept = summ$intercept, color = "black") +
      # Experiment-specific effect sizes
      geom_point(shape = 0) +
      # Styling
      scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
      scale_y_reverse() +
      coord_cartesian(
        xlim = c(-2.5, 2.5),
        ylim = c(max_se, 0),
        expand = FALSE
      ) +
      labs(
        x = expression("Hedges'" ~ italic("g")), y = "Standard error",
        fill = "Significance level"
      ) +
      theme_classic() +
      theme(
        axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "Helvetica", color = "black"),
        axis.ticks = element_line(color = "black"),
        legend.position = "none",
        text = element_text(family = "Helvetica", color = "black")
      )
  }
) -> plots_funnel

@@

## Data and code availability

The data and code necessary to reproduce the analyses presented here are publicly accessible at the following URL: [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).

### 2022-07-15 supplement.Rmd
Update for re-submission

# Add footnotes
tabs8$` `[8] <- str_c(tabs8$` `[8], "\\textsuperscript{a}")
tabs8$` `[9] <- str_c(tabs8$` `[9], "\\textsuperscript{b}")
tabs8$` `[10] <- str_c(tabs8$` `[10], "\\textsuperscript{c}")
tabs8$` `[11] <- str_c(tabs8$` `[11], "\\textsuperscript{d}")

# Display the table
apa_table(
  tabs8,
  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = an uninformative (uniform) prior on the mean effect, ",
    "\\textsuperscript{b} = an informative (normal) prior on the mean effect, ",
    "\\textsuperscript{c} = an uninformative (uniform) prior on the standard deviations, ",
    "\\textsuperscript{d} = an informative (Student-$t$) prior on the standard deviations."
  ),
  font_size = "scriptsize", landscape = TRUE, escape = FALSE,
  align = "llrrrrrrr"
)
```

>>>>

# Add footnotes
colnames(tabs8)[7] <- str_c(colnames(tabs8)[7], "\\textsuperscript{a}")
tabs8$` `[8] <- str_c(tabs8$` `[8], "\\textsuperscript{b}")
tabs8$` `[9] <- str_c(tabs8$` `[9], "\\textsuperscript{c}")
tabs8$` `[10] <- str_c(tabs8$` `[10], "\\textsuperscript{d}")
tabs8$` `[11] <- str_c(tabs8$` `[11], "\\textsuperscript{e}")

# Display the table
apa_table(
  tabs8,
  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = violation of expectation, ",
    "\\textsuperscript{b} = an uninformative (uniform) prior on the mean effect, ",
    "\\textsuperscript{c} = an informative (normal) prior on the mean effect, ",
    "\\textsuperscript{d} = an uninformative (uniform) prior on the standard deviations, ",
    "\\textsuperscript{e} = an informative (Student-$t$) prior on the standard deviations."
  ),
  font_size = "scriptsize", landscape = TRUE, escape = FALSE,
  align = "llrrrrrrr"
)
```
